A causal analysis of the effect of abortion policies on maternal mortality

### 2022-06-08 PaperAnalysis.Rmd
Emails

### Theorethical estimands

@@

* Helena Bakic (bakic.helena@outlook.com): Empirical estimation, Identification, Heterogeinity of effects, Analysis
* Anna-Lisa Wirth (213286@mds.hertie-schoo.org): Background, Unmeasured Confounding, Missing Data, Sensitivity Analysis, Analysis and Conclusion 
* Ángela Duarte Pardo: Data Cleaning, G-separation, Methodology, Modelling and Analysis

>>>>

### Theoretical estimands

@@

* Helena Bakic (bakic.helena@outlook.com): Empirical estimation, Identification, Heterogeneity of effects, Analysis
* Anna-Lisa Wirth (213286@mds.hertie-school.org): Background, Unmeasured Confounding, Missing Data, Sensitivity Analysis, Analysis and Conclusion 
* Ángela Duarte Pardo (214566@mds.hertie-school.org): Data Cleaning, G-separation, Methodology, Modelling and Analysis
